\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{\center{Practice Exercises}}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item Name some of the methods of jQuery used to provide effects?\underline{\hspace{3cm}}.
\item Which jQuery method is used to hide selected elements?\underline{\hspace{3cm}}.
\item Which jQuery method is used to switch between adding/removing one or more classes (for CSS) from selected elements?\underline{\hspace{3cm}}.
\item The \texttt{hide()} function hides an element by setting “display” inline style attribute of that element to ``none''. (True / False)\underline{\hspace{3cm}}.
\item The \texttt{show()} method can show a hidden element. (True / False)\underline{\hspace{3cm}}.
\item The functionality of \texttt{toggle()} method is\underline{\hspace{3cm}}.
\item The\underline{\hspace{3cm}}function slides down a hidden HTML element, so it becomes visible.
\item The\underline{\hspace{3cm}}function shows an HTML element if it is hidden, or hides it if visible.
\item \texttt{fadeToggle()} and \texttt{slideToggle()} are having the same functionality. (True / False
)\underline{\hspace{3cm}}.
\item Which function enables you to fade an HTML element partially in or out, making it transparent?\underline{\hspace{3cm}}.
\item SlideToggle attaches two functions, what are they?\underline{\hspace{3cm}}.
\item FadeToggle attaches two functions, what are they?\underline{\hspace{3cm}}.
\item Possible values of the speed parameter of \texttt{fadeToggle()} function are\underline{\hspace{3cm}}.
\item Speed is an optional parameter in \texttt{fadeToggle()} function?. (Yes / No)\underline{\hspace{3cm}}.
\end{enumerate}
\subsection*{Exercises}
\begin{itemize}
\item Write the expected output, or compiler errors if any, for each of the following programs in the box provided below each program.
\item Then execute the programs and check your answers.
\item Then answer the questions given below.
\end{itemize}
\begin{description}
\item[program 1]\
\begin{lstlisting}
<script>
    $(document).ready(function() {
        $(``#jbtnShow'').click(function() {
            $(``#jShow'').show(``slow'');
        });
        $(``#jbtnHide'').click(function() {
            $(``#jShow'').hide();
        });
    });
</script>
<div id = ``jShow'' class = ``demoBlock'' style = ``display:none;''>
    This is the hiddent text</div>
    <input type = ``button'' value = ``Show Text'' 
    id = ``jbtnShow'' />
    <input type = ``button'' value = ``Hide Text'' 
    id = ``jbtnHide'' /> |
    <input type = ``button'' value = ``Show Fast'' 
    id = ``jbtnShowFast'' />
    <input type = ``button'' value = ``Hide Normal'' 
    id = ``jbtnHideNormal'' />
</div>
\end{lstlisting}

\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What will be the output for the above code snippet?
\item When will \texttt{show()} and \texttt{hide()} functions get's invoked?
\item What happens if line 4 is changed to \texttt{\$(``\#jShow'').show(``fast'');}?
\item What happens if value \texttt{``normal''} is passed to \texttt{hide()} function at line 7?
\end{enumerate}

\item[Program 2]\
\begin{lstlisting}
<script>
    $(``#jbtnSCount'').click(function() {
        $(``#jShow'').show(3000);
    });
    $(``#jbtnHCount'').click(function() {
        $(``#jShow'').hide(3000);
    });
    $(``#jbtnTog'').click(function() {
        $(``#jShow'').toggle(``slow'');
    });
</script>
<body>
    <input type = ``button'' value = ``Show''  id = ``jbtnSCount'' />
    <input type = ``button'' value = ``Hide''  id = ``jbtnHCount'' /> 
    <input type = ``button'' value = ``Click''  id = ``jbtnTog'' />
</body>
\end{lstlisting}

\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item When will \texttt{toggle()} function get's invoked?
\item What will be the output for the above code snippet?
\item What does \texttt{show(3000)} and \texttt{hide(3000)} will do in the above code snippet?
\item What happens if parameter value of \texttt{toggle()} function is changed to 3000 at line 9?
\end{enumerate}
\item [Program 3]\ 
\begin{lstlisting}
<script>
    $(document).ready(function() {
        $(``#jbtnSlideDown'').click(function() {
            $(``#jdivWelcome'').slideDown();
        });
        $(``#jbtnSlideUp'').click(function() {
            $(``#jdivWelcome'').slideUp();
        });
    });
</script>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Write HTML declaration for the above code snippet?
\item When will \texttt{slideDown()} and \texttt{slideUp()} be executed?
\item What happens if the value \texttt{``normal''} is passed to \texttt{slideDown()} function at line 4?
\item What happens if the value \texttt{``fast''} is passed to \texttt{slideUp()} function at line 7?
\end{enumerate}

\item [Program 4]\ 
\begin{lstlisting}
$(``#jbtnSlideToggle'').click(function() {
    $(``#jdivWelcome'').slideToggle();
});
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What does \texttt{slideToggle()} will do in the above code snippet?
\item What does \texttt{\$(``\#jbtnSlideToggle'')} wil select?
\item What does \texttt{\$(``\#jdivWelcome'')} wil select?
\item Will \texttt{slideToggle()} have the same functionalities of both \texttt{slideDown()} and \texttt{slideUp()}?
\item What happens if the value \texttt{``fast ''} is passed to \texttt{slideToggle()} at line 2?
\end{enumerate}

\item [Program 5]\ 
\begin{lstlisting}
<script>
    $(document).ready(function() {
        $(``#btnFadeIn'').click(function() {
            $(``#jDivFade'').fadeIn();
        });
        $(``#btnFadeOut'').click(function() {
            $(``#jDivFade'').fadeOut();
        });
        $(``#btnFadeLimited'').click(function() {
            $(``#jDivFade'').fadeTo(``slow'', 0.40);
        });        
    });
</script>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Write HTML declaration for the above jQuery code?
\item What does \texttt{fadeIn()} and \texttt{fadeOut()} will do in above code snippet?
\item What is the type of second paraemter in \texttt{fadeTo()} function at line 10?
\end{enumerate}

\item [Program 6]\ 
\begin{lstlisting}
<script src = ``jquery−1.11.1.js''></ s c r i p t>
<script>
    $(document).ready(function() {
        $(``#flip'').click(function(event) {
            $(``#para1'').css(``color'', ``green'');
            $(``#para1'').css(``font−weight'', ``bold'');
            $(``#panel'').fadeToggle(2000);
        });
    });
</script>
<body>
    <p id = ``para1''>The only thing that interferes with 
    my learning is my education.
    <span style = ``color : red''>``Albert Einstien''</span><p>
    <div id = ``panel''>Click to slideDown</div>
    <button id = ``flip''>Slide Effect</button>
</body>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What will be the output for the above code snippet?
\item What does \texttt{\$(``\#para1'')} wil select?
\item What does \texttt{\$(``\#panel'')} wil select?
\item Will \texttt{fadeToggle()} have the same functionalities of both \texttt{fadeIn()} and \texttt{fadeOut()}?
\item What happens if the value \texttt{``fast ''} is passed to \texttt{fadeToggle()} at line 7?
\item What is the difference between \texttt{slideToggle()} and \texttt{fadeToggle()}?
\end{enumerate}

\end{description}
\subsection*{Additional Exercises}
\begin{enumerate}
\item Write code, so that user can click the button (the h2 tag in this case) and the instructions will fade in/fade out of view in half a second.
\begin{lstlisting}
<body>
    <h2 id = ``button''>Instructions</h2>
    <div id = ``instructions''>
        <p>Turn the knob</p>
    </div>
</body>
\end{lstlisting}
\item Write jQuery code, When someone clicks on a selector, you want a (currently invisible) DIV with an ID of submenu to appear.  Clicking the selector again hides the submenu.
\item When someone mouses over the h1 tag, you want a (currently invisible) div with an ID of submenu to appear. Moving the mouse off the h1 tag hides the submenu again. Write the code with anonymous functions.
\item Fade the \texttt{$<$p$>$} tag below on to the screen over the course of three seconds.
\begin{lstlisting}
<!DOCTYPE html>
<html>
    <head>
        <title>Fade In</title>
    </head>
    <body>
        <p>This text will fade in over three seconds</p>
    </body>
</html>
\end{lstlisting}
\end{enumerate}
\end{document}
