\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{\center{Practice Exercise}}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item How do you check validations in Javascript?\underline{\hspace{3cm}}.
\item How do you get field value in Javascript?\underline{\hspace{3cm}}.
\item How to validate a email-address, in form using Javascript?\underline{\hspace{3cm}}.
\item In which part does the form validation occur?\underline{\hspace{3cm}}.
\item What would happen if the data in the client had been wrong?\underline{\hspace{3cm}}.
\item  What is the purpose of the basic validation?\underline{\hspace{3cm}}.
\item What is the purpose of data format validation?\underline{\hspace{3cm}}.
\item Which is the function that is called to validate a data?\underline{\hspace{3cm}}.
\item The\underline{\hspace{3cm}}event can be used to call a function to check all fields that require validation before sending a form.
\item The validation function must return a \texttt{true} if ready to submit or a \texttt{false} if not ready.(Yes / No)\underline{\hspace{3cm}}.
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Write the expected output, or compiler errors if any, for each of the following programs in the box provided below each program.
\item Then execute the programs and check your answers.
\item Then answer the questions given below.
\end{itemize}
\begin{description}
\item[program 1]\
\begin{lstlisting}
<script type = ``text/JavaScript'' language = ``JavaScript''>
    function validate() {
        var name = document.getElementById(``custname'').value;
        if (name == ``'') {
             alert(``Your name is required'');
             return false;
        }
    }
</script>
\end{lstlisting}

\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What happens if name = ``''?
\item What happens if name = ``WISE''?
\item What happens if name = ``12@34\&5''?

\end{enumerate}

\item[Program 2]\
\begin{lstlisting}
<form method = ``post'' action = ``mailto:asokanp@tswise.com">
    <p>Name: <input type = ``text'' size = ``65''></p>
    <p>E-mail Address:  <input type = ``text'' size = ``65'' ></p>
    <p>Telephone: <input type = ``text'' size = ``65''><br>
        <input type = ``checkbox''> Please do not call me.</p>
    <p> What can we help you with?
        <select type = ``text'' value = ``''>
            <option>  </option>
            <option>Customer Service</option>
            <option>Question</option>
            <option>Comment</option>
            <option>Consultation</option>
            <option>Other</option>
        </select></p>
    <p>Comments:  <textarea cols=``55''>  </textarea></p>
    <p><input type=``submit'' value=``Send'' name=``submit''><br>
    <input type=``reset'' value=``Reset'' name=``reset''></p>
</form>
\end{lstlisting}

\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Write javascript form validations for the above HTML code?
\end{enumerate}
\item [Program 3]\ 
\begin{lstlisting}
<script type = ``text/JavaScript'' language = ``JavaScript''>
    if (email.value == ``'') {
        window.alert(``Please enter a valid e-mail address.'');
        email.focus();
        return false;
    }
    if (email.value.indexOf(``@'', 0) < 0) {
        window.alert(``Please enter a valid e-mail address.'');
        email.focus();
        return false;
    }
    if (email.value.indexOf(``.'', 0) < 0) {
        window.alert(``Please enter a valid e-mail address.'');
        email.focus();
        return false;
    }

</script>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What is happening in the above code snippet?
\item What will happen if the value of email is abc@xyz.com?
\item What \texttt{if} returns for the empty value of email? 
\end{enumerate}
\item [Program 4]\
\begin{lstlisting}
<body bgcolor = ``yellow''>
        <form action = ``Response.html''>
            Username: <input type = ``text'' name = ``uname''\>
            Password: <input type = ``password'' name = ``pass''\>
            Email-Id: <input type = ``text'' name = ``email''\>
            Phone-No: <input type = ``text'' name = ``phno''\>
            <input type = ``submit'' value = ``Submit''\>
        </form> 
    </body>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Write form validations for the above HTML code using javascript?
\end{enumerate}
\end{description}

\subsection*{Additional Exercises}
\begin{enumerate}
\item Write the JavaScript function \texttt{validate()} that generates a JavaScript alert message \texttt{``Your name is required''} and returns false if the Name text input field has not been filled in, otherwise it returns true.
\item Add the JavaScript code to make Email and Website required fields and let Company and Telephone be optional fields.
\item Write the JavaScript code that uses a regular expression to validate that the user name consists of only letters or the blank space character. Generate an alert message if the name is incorrect.
\item Write the JavaScript code that uses a regular expression to validate that the Email consists aa@bb.cc where aa, bb, and cc are one or more alphanumeric characters.
\item Write the JavaScript code that uses a regular expression to validate that the optional Telephone field is in the pattern ddd-ddd-dddd or ddd-dddd where d is any digit.
\item Write the JavaScript code that uses a regular expression to validate that the Website field is in the pattern http://aaa.bbb.ccc where aaa, bbb, ccc, are one or more alphanumeric characters.
\item Create a javascript function which returns true or false depending on the validation.
\end{enumerate}
\end{document}
