\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{Practice Exercise}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item Class is specified by including a period\underline{\hspace{3cm}}before the selector name.
\item The syntax for declaring a Class selector is\underline{\hspace{3cm}}.
\item You can use the same class on multiple elements.( True / False )\underline{\hspace{3cm}}.
\item You can use multiple classes on the same element.(True / False)\underline{\hspace{3cm}}.
\item ID is specified by\underline{\hspace{3cm}}before the selector name.
\item The syntax for declaring an ID selector is\underline{\hspace{3cm}}.
\item Each element can have only one ID.(True / False)\underline{\hspace{3cm}}.
\item Each page can have only one element with that ID.(True / False)\underline{\hspace{3cm}}.
\item .para represents\underline{\hspace{3cm}}.
\item \#para represents\underline{\hspace{3cm}}.
\item The difference between ID and class is that an ID selector can be called only once in a document, while a class selector can be called multiple times in a document.(True / False)\underline{\hspace{3cm}}.
\item Which selectors are used when you want to redefine the general look for an entire HTML tag?\underline{\hspace{3cm}}.
\item Which selectors are used when you want to define a style that does not redefine an HTML tag entirely?\underline{\hspace{3cm}}.
\item $<$DIV$>$ is what kind of tag ?\underline{\hspace{3cm}}.
\item When referring to a Class selector you simply add the class to what?\underline{\hspace{3cm}}.
\item Selectors that will share some of the same styles can be\underline{\hspace{3cm}}.
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Write the expected output, or compiler errors if any, for each of the following programs in the box provided below each program.
\item Then execute the programs and check your answers.
\item Then answer the questions given below.
\end{itemize}
\begin{description}
\item[program 1]\
\begin{lstlisting}
<h1 class = ``something''>Read books, take notes and study</h1>
<p class = ``something''>Read, read, read</p>
<p>But spend more time hacking, hacking, hacking</p>
<p class = ``something''>This is</p>
<p>the story of a girl</p>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Color all page elements with the class ``something'' \texttt{red} in the above HTML snippet?
\item Color the $<$p$>$ tag with the class ``something'' \texttt{blue} in the above HTML snippet?
\item Color all the $<$p$>$ tags in the above html snippet \texttt{green}?
\end{enumerate}

\item[Program 2]\
\begin{lstlisting}
<h5 id = ``bling''>Assets</h5>
<p>Liabilities</p>
<strong class = ``meaning-of-life''>Equity</strong>
<h5>Current assets</h5>
<strong>Quick ratio</strong>
<p id = ``blah''>This is something</p>
<p>I like Ethiopian food</p>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Color the element with the id tag of ``blah'' \texttt{red} in the above HTML snippet?
\item Style the ``bling'' id, $<$p$>$ tag, and ``meaning-of-life'' class to be \texttt{blue} in the above HTML snippet?
\item Color all the $<$p$>$ tags in the above html snippet \texttt{green}?
\end{enumerate}


\item [Program 3]\
\begin{lstlisting}
<html>
    <head>
        <title>Keesha</title>
    </head>
    <body>
        <h1>Tik Tok</h1>
        <p>I like <strong>mango</strong> and 
        <strong>drink</strong> </p>
    </body>
</html>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Identify the children elements of the $<$body$>$ tag?
\item Identify the children elements of the $<$p$>$ tag?
\item Identify the parent of the $<$h1$>$ tag?
\item Identify the siblings of the $<$head$>$ tag?
\end{enumerate}

\item [Program 4]\
\begin{lstlisting}
<div class = ``something''>
    <p>In Jersey, we are <strong>STRONG</strong> </p>
    <p>In US, we have <strong>strong</strong> personalities </p>
</div>
<p>In Ireland, we have a <strong>strong</strong> will</p>
<h1>Tik Tok <strong>Great songs!</strong></h1>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Color the text in the $<$strong$>$ tags contained in the \texttt{.something} class \texttt{red}, but do not color the other $<$strong$>$ tags?
\item Color the text ``Great songs!'' \texttt{red} in the above HTML snippet?
\item Increase teh font size of all the $<$p$>$ tags?
\item Apply the font family for all the tags in the above HTML snippet using CSS?
\end{enumerate}

\item [Program 5]\
\begin{lstlisting}
<a href = ``http://www.talentsprint.com/WISE''>Modules</a>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Color the above link \texttt{red} if the user has not visited it yet?
\item Color the above link \texttt{green} if the user has already visited it?
\item Color the above link \texttt{pink} if the user has the mouse over the link?
\item Make the background color \texttt{blue} when a use clicks on a link?
\end{enumerate}

\item [Program 6]\
\begin{lstlisting}
<ul class = ``majors''>
    <li>Math</li>
    <li>Bio</li>
    <li>Chemistry</li>
</ul>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Color the math majors \texttt{green}, but don't color the other $<$li$>$s?
\item Color the chemistry $<$li$>$ \texttt{red}, but don't color the other $<$li$>$s?
\end{enumerate}

\item [Program 7]\
\begin{lstlisting}
h1.highlight {
    background: yellow;
    color: #000;
 }
#content p {
}
#footer p {
}
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What would the html tag look like for the above CSS snippet to be applied?
\item Why would we use the above two \texttt{p} selectors?
\item Apply the font style for all the selectors in the above CSS snippet?
\end{enumerate}

\end{description}
\subsection*{Additional Exercises}
\begin{enumerate}
\item Apply the style for a selector within a selector.
\item Write HTML and CSS code to assign multiple classes to an element and also apply the style for them?
\item Write HTML and CSS code to describe Grouping selectors.
\end{enumerate}
\end{document}
