\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{WorkBook-5}
\subsection*{Practice Exercise}
\begin{enumerate}\itemsep10pt
\item Table headings are defined with the \underline{\hspace{3cm}} tag.
\item Which tag is used to add a row in a table? \underline{\hspace{3cm}}
\item Which attribute is used to span a cell into multiple rows? Which attribute is used to span a cell into 
\item Write the HTML to left-align the content inside a tablecell \underline{\hspace{3cm}}
\item Which tag is used to define a table caption? \underline{\hspace{3cm}}
\item Which HTML attribute is used along with td tag to merge two cells horizontally? \underline{\hspace{3cm}}
\item The \underline{\hspace{3cm}} attribute adds space within each cell in a table.
\item The \underline{\hspace{3cm}} tag is used to add a data to a table.
\item Which attribute is used to span a cell into multiple columns? \underline{\hspace{3cm}}
\item Which attribute is used to crerate a table border? \underline{\hspace{3cm}}
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Complete the following  exercises

\item[Exercise-1]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a company web site with a home page and links to Home,About US,Clients,Products and Contact.
\item Add content about each link.
\end{enumerate}

\item[Exercise-2]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a html page about UML Behavioral Modles
\item Explain what is a Behavioral Model
\item Create a table with columns as Diagram Type, Details, Explanation as a link.
\item In the Explanation column add link to each diargam
\item In the Explanation link page add content with headings Use,Example Diagram,Tools,Notes.
\end{enumerate}

\item[Exercise-3]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Design your class room time table.
\end{enumerate}
\end{itemize}

\subsection*{Additional Exercises}
\begin{enumerate}
\item Create a table showing the population growth rate for countries around the world.
Give the table Heading as ``Population Growth Rate'' and Rank,Country,Rate as colums
\item Create a do-list table.
\item Construct a pair of tables side by side within another table. Using the table attributes of cellspacing, cellpadding and border,and center it across the width of the page.
\end{enumerate}
\end{document}
