\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{Practice Exercise}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item What is the HTML5 element for playing video files? \underline{\hspace{2cm}}
\item Which attribute is used to play the video continuously? \underline{\hspace{2cm}}
\item Write three supported file formats for the $<$audio$>$ element \underline{\hspace{3cm}}
\item Which attribute specifies that the audio will start over again, every time it is finished? \underline{\hspace{2cm}}
\item Which attribute specifies the URL of the audio file? \underline{\hspace{2cm}}
\item Which attribute specifies the address of the external file to embed? \underline{\hspace{2cm}}
\item The \underline{\hspace{2cm}} and  \underline{\hspace{2cm}} attributes are used to specify the height and width of the video player
\item The \underline{\hspace{2cm}} attribute adds video controls, like play, pause, and volume.
\item Which attribute is used to mute audio output? \underline{\hspace{2cm}}
\item Which attribute is used to play the media automatically when the page is loaded? \underline{\hspace{2cm}}
\item The \underline{\hspace{2cm}} attribute to display a frame of the video
\item When autoplay attribute has defined in $<$video$>$ element then \underline{\hspace{2cm}} attribute is ignored.
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Complete the following  exercises

\item[Exercise-1]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a HTML page with ``C Programming language'' as a title and display the text about c language.
\item Create a navigation bar on the left side of the homepage and list three important concepts of c language as a links.
\item Each link shoud open in a new page and has to play an audio about the concept at least for 3 minutes
\end{enumerate}

\item[Exercise-2]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a HTML page about UML Interation Diagrams 
\item Add images about each diagram and explain the importance
\end{enumerate}

\item[Exercise-3]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a Educational portal site with a logo and title as ``Educare'' in the center of the Homepage and play a video about the site for three minutes in the homepage.
\item Display student testimonials in the Home page 
\item Create links to Home, Technologies, About, Staff, Contact in the home page and add content and images in the respective pages.
\end{enumerate}
\end{itemize}

\subsection*{Additional Exercises}
\begin{enumerate}
\item Create an Admission page add the fields relatd to the personal information and education details.
\item Create a web page with a heading ``My blog about my life''and display a menu with items Today,Yesterday,Last week,Archives as a links and add the content.
\item Create a web site with a name ``Career Advice'' with a logo and add a caption.Add links to Resume Preparation, Frequently asked questions, Interview preparation and explain.
\end{enumerate}
\end{document}
