\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{Practice Exercise}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item Where in an HTML document is the correct place to refer to an external style sheet?\underline{\hspace{3cm}}.

\item Which HTML tag is used to define an internal style sheet?\underline{\hspace{3cm}}.

\item How do you add a background color for all \texttt{$<$h1$>$} elements?\underline{\hspace{3cm}}.

\item How do you change the text color of an element?\underline{\hspace{3cm}}.

\item What is the correct CSS syntax for making all the \texttt{$<$p$>$} elements bold?\underline{\hspace{3cm}}.

\item How do you change the font of an element?\underline{\hspace{3cm}}.

\item How do you make the text bold?\underline{\hspace{3cm}}.

\item How do you change the left margin of an element?\underline{\hspace{3cm}}.

\item Which property is used to change the background color?\underline{\hspace{3cm}}.

\item Which CSS property controls the text size?\underline{\hspace{3cm}}.

\item To define the space between the element's border and content, you use the padding property, but are you allowed to use negative values? (Yes / No)\underline{\hspace{3cm}}.

\item What does CSS stand for?\underline{\hspace{3cm}}.

\item What is the correct HTML for referring to an external style sheet?\underline{\hspace{3cm}}.

\item Which HTML attribute is used to define inline styles?\underline{\hspace{3cm}}.

\item How do you insert a comment in a CSS file?\underline{\hspace{3cm}}.

\item How do you display hyperlinks without an underline?\underline{\hspace{3cm}}.

\item \texttt{text-align: center} will always center your text. (Yes / No)\underline{\hspace{3cm}}.

\item What are the four kinds of links?\underline{\hspace{3cm}}.

\item What property do you use to create spacing between HTML elements?\underline{\hspace{3cm}}.

\item What property would you use to change the list style to show roman numerals instead of normal numbers?\underline{\hspace{3cm}}.

\item What property can you use to set the spacing in between lines of text?\underline{\hspace{3cm}}.

\item Which property is necessary to set an image in the background?\underline{\hspace{3cm}}.

\item How would you style table rows to have alternating background colors?\underline{\hspace{3cm}}.

\item What property would you use to change the size of an HTML element's border?\underline{\hspace{3cm}}.

\item If you want to add italics, what CSS code do you use?\underline{\hspace{3cm}}.

\item How do you make a list that lists its items with squares?  \underline{\hspace{3cm}}.

\item What is the correct CSS syntax for making all the $<$span$>$ elements bold?\underline{\hspace{3cm}}.

\item In the following code snippet, what value is given for the left margin:\underline{\hspace{3cm}}.
\begin{lstlisting}
margin: 5px 10px 3px 8px;
\end{lstlisting}

\item Which snippet of CSS is commonly used to center a website horizontally?\underline{\hspace{3cm}}.

\item How do you make a list not display bullet points?\underline{\hspace{3cm}}.

\item What is the correct Syntax for importing a stylesheet in CSS?\underline{\hspace{3cm}}.

\item How do you make each word in a text start with a capital letter?\underline{\hspace{3cm}}.

\item What is the correct CSS syntax for making all the $<$p$>$ tag's font size 14px?\underline{\hspace{3cm}}.

\item A declaration is terminated by\underline{\hspace{3cm}}.

\item How do you insert padding so that it is:
\begin{lstlisting}
10 pixels at the top
15 pixels at the bottom
5 pixels at the right
10 pixels to the left
\end{lstlisting}
\underline{\hspace{3cm}}.
\item What is the correct CSS syntax to change the font name?\underline{\hspace{3cm}}.

\item In the following code snippet, which part represents the property?\underline{\hspace{3cm}}.
\begin{lstlisting}
table {color: blue;}
\end{lstlisting}

\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Write the expected output, or compiler errors if any, for each of the following programs in the box provided below each program.
\item Then execute the programs and check your answers.
\item Then answer the questions given below.
\end{itemize}
\begin{description}
\item[program 1]\
\begin{lstlisting}
<header><h1>Header Text</h1></header>
<article><h1>Aritcle Text</h1></article>
\end{lstlisting}
\AnswerBox

\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item How can we set the color \texttt{red} for text which is placed only in the $<$header$>$ tag?
\item How can we set the color \texttt{green} for all the tags in the above code snippet?
\end{enumerate}
\item[Program 2]\
\begin{lstlisting}
<ul>
    <li>Java</li>
    <li>Python</li>
    <li>C</li>
    <li>GIT</li>
</ul>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item How can we use an image instead of the marker symbol?
\item How do you make a list that lists its items with squares?
\item What is the CSS code for making the $<$ul$>$ tag's font size 18px?
\end{enumerate}

\item [Program 3]\ Simplify the following CSS code.
\begin{lstlisting}
<link type = ``text/css'' href = ``style.css''/>
<style>
    div {
        height: 10px;
    }
</style>
<div></div>

And ``style.css'' looks like
div {
    height: 20px;
}
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What will be the height of the element $<$div$>$?
\end{enumerate}

\item [Program 4]\ 
\begin{lstlisting}
<style type = ``text/css''>
    body {
        font-size: 24pt;
    }
    p {
        font-size: 50%;
    }
    span {
        font-size: 1.5em;
    }
</style>
<p><span>WISE</span></p>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item What size will have the WISE?
\item What is the CSS code to change the WISE in bold?
\item Color the WISE \texttt{yellow} using CSS code?
\end{enumerate}

\item [Program 5]\
\begin{lstlisting}
<ul>
    <li><span>Tomato</span></li>
    <li><span>Potato</span></li>
    <li><span>Carrot</span></li>
</ul>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item How can we make the color of the markers in the list different from the color of the text?
\item How do you make a list not display bullet points?
\end{enumerate}


\item [Program 6]\
\begin{lstlisting}
<a href = ``#''>link</a>
\end{lstlisting}
\AnswerBox
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item How can we add a dashed underline to links?
\item How do you display link without an underline?
\end{enumerate}


\end{description}
\subsection*{Additional Exercises}
\begin{enumerate}
\item Apply the CSS style to HTMl document for the following example. We will use a list of names. The names are all marked with $<$li$>$ (list-item). Let's say that we want names to be capitalized and headlines to be presented in uppercase letters.
\item Apply CSS Border style (inline) to a table.
\item Fieldset element with CSS styling affecting margin (outside) and padding (inside).
\end{enumerate}
\end{document}
