\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{Practice Exercise}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item Write the DOCTYPE declaration for HTML5 \underline{\hspace{3cm}}
\item The HTML5 specification has been finalized.[True / False]
\item What is the previous version of HTML, prior to HTML5? \underline{\hspace{3cm}}
\item The \underline{\hspace{3cm}} declaration indicates the version of HTML to the browser.
\item The \underline{\hspace{2cm}} attribute of $<$embed$>$ tag is used to specify the address of the external file to embed.
\item The \underline{\hspace{2cm}} attribute is used to give the address of the resource in $<$iframe$>$.
\item The \underline{\hspace{2cm}} tag is used to embed the content from plugin.
\item The \underline{\hspace{3cm}} tag defines an image in an HTML page.
\item The \underline{\hspace{2cm}} attribute specifies the destination of a link in $<$a$>$ tag.
\item Write any three new elements of HTML5 \underline{\hspace{3cm}}
\item The \underline{\hspace{2cm}} attribute specifies an alternate text for an image.
\item What are the two required attributes of $<$img$>$ tag \underline{\hspace{2cm}}
\item The \underline{\hspace{2cm}} attribute of $<$embed$>$ specifies the MIME type of the embedded content.
\item The \underline{\hspace{2cm}} attribute of $<$img$>$ tag specifies the URL of an image
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
\item Complete the following  exercises
\item[Exercise-1]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a Homepage about HTML with title ``Web Designing using html'' with a logo and expalin the introduction to HTML 
\item Create a Navigation bar with links to the topics ``HTML Basics'',``Heading Tags in html'',``Working With Links'',``Working with images''.
\item Explain each topic with one example.
\end{enumerate}
\item[Exercise-2]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a website with the title ``E-learning for kids'' with a logo and add a caption as ``foundation for future'' 
\item Add navigation links for Maths,Science,Environmental Skills,Computer Skills.
\item In each subject link add three exercise questions.
\end{enumerate}
\item[Exercise-3]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Make a page with a heading ``Programming In c'',make the heading large, bold, italic and center it across the top of the page.
\item Write a short paragraph or two telling a little about Introdcution to c ,highlight important text in italics.
\item Using an unordered bulleted list, list five important concepts that you would most like to put and explain.
\end{enumerate}
\end{itemize}

\subsection*{Additional Exercises}
\begin{enumerate}
\item Create a shopping web site with the name ``Easy Shopping'' with a logo and navigation bar with three links to Mobiles \& Electronics,  Clothing \& Watches and  Books,Video Games\&Media and add images of products and prices each category in the links.
Show latest discounts of different products in the home page.
\item Create a registration page with First Name,Last Name,Gender,Email,Mobile Number,Date of Birth,UserName,Password,Address,Zip code as a fields using HTML5 tags.
%\item Create your Resume using html tags start with your name,address and phone number on top of the page.Write an Objective and %Academics.Lastly add Achiements and Personal information.
\item Create a your resume strating with your name,address and phone number in the center of the page. Write Objective,Education,Experience,Computer Skills,Achiements,Personal information.
\end{enumerate}
\end{document}
