\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\lstset{language=C,numbers=left,numberstyle=\tiny,numbersep=10pt,showstringspaces=false}
\usepackage{array}
\usepackage{enumitem}

\def\AnswerBox{\fbox{\begin{minipage}{4in}\hfill\vspace{0.5in}\end{minipage}}}

\begin{document}
\section*{\center{Practice Exercises}}
\subsection*{Review Questions}
\begin{enumerate}\itemsep10pt
\item JavaScript is inserted into HTML page by using \underline{\hspace{3cm}}
%\item Which html tag contain javascript code? \underline{\hspace{3cm}}
\item Where is the correct place to insert a JavaScript in a html document? \underline{\hspace{3cm}}
\item How to write ``Hello World'' in an alert box? \underline{\hspace{3cm}}
\item The \underline{\hspace{3cm}} function will prints the output on the document.
\item Variables are declared with the \underline{\hspace{3cm}} keyword.
\item Which event will occur when an element gets focus? \underline{\hspace{3cm}} 
\item Which popup box is used to display a dialog box containing an application-defined message? \underline{\hspace{2cm}} 
\item Window.prompt() method return true or false value? (Yes / No).
\item Which popup box is used to verify something from user? \underline{\hspace{2cm}}
\item Window.alert() is used to allow user to enter something? (True / False).
\item Variable names in javascript can begin with a number? (True / False).
\item What are the three main primary data types? \underline{\hspace{2cm}}
\end{enumerate}

\subsection*{Exercises}
\begin{itemize}
%\item Write the expected output for each of the following programs in the box provided below each program.
%\item Then execute the programs and check your answers.
%\item Then answer the questions given below.
\item Complete the following  exercises
\item[Exercise-1]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a page with JavaScript prompt the user for their name.
\item Use a pop-up box to welcome the user by name.
\item Display the current date on the page in the following format: October 30, 2000.  
\end{enumerate}
\item[Exercise-2]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Create a calculator application with an input and buttons for the operations.
\item Add the functions for the each operation.
\item Create an event listener for the button, and when it's clicked, find the value of the appropriate input and show the result of the calculation.
\end{enumerate}
\item[Exercise-3]\
\begin{enumerate}[label=\bfseries Q\arabic*:]\itemsep10pt
\item Write a JavaScript program to get the current date. 
Expected Output : mm-dd-yyyy, mm/dd/yyyy or dd-mm-yyyy, dd/mm/yyyy 
\end{enumerate}
\end{itemize}

\subsection*{Additional Exercises}
\begin{enumerate}
\item Write a JavaScript program where the program takes a random integer between 1 to 10, the user is then prompted to input a guess number. If the user input matches with guess number, the program will display a message ``Good Work'' otherwise display a message ``Not matched''. 
%\item Write a script that contains a button and a counter in a div. The button should increment the counter each time it is clicked.
\item Write a web app to convert time units. User should enter time in seconds, minutes or hours, and convert to all the others
\item Write a web app to convert distance units. Available units: meters, kilometers and miles. 
\item Write a JavaScript program to print the contents of the current window.
\item Write a JavaScript program to convert temperatures to and from celsius, fahrenheit.
\end{enumerate}
\end{document}
